# PA1_template
==============

## Loading and prepocessing the data

```{r}
setwd("C:/DR for 3 month")
activitydata <- read.csv("activity.csv", header=TRUE)
activitydata <- data.frame(activitydata)
```

## Mean total number of steps taken per day 

### Calculate total steps taken per day

```{r}
totalsteps <- aggregate(activitydata$steps,
                        by = list(activitydata$date),
                        FUN = sum,
                        na.rm = TRUE)

names(totalsteps) <- c("date","total")
```

### Histogram, Mean, and Median

```{r}
hist(totalsteps$total, 
     main = "Total number of steps taken each day",
     xlab = "Number of steps")

mean(totalsteps$total)
median(totalsteps$total)
```



## Average daily activity pattern

```{r}
meandata <- aggregate(activitydata$steps,
                        by = list(activitydata$interval),
                        FUN = mean, 
                        na.rm = TRUE)
names(meandata) <- c("interval","mean")
```

### create plot

```{r}
plot(meandata$interval, meandata$mean, type="l",
     xlab = "5-minute interval",
     ylab = "average number of steps",
     main = "Average daily activity pattern")
max_interval <- meandata[which.max(meandata$mean),]
max_interval
```

## Inputing missing values

### calculate and report the total number of missing values

```{r}
missingvalues <- sum(is.na(activitydata$steps))
```

There are `r missingvalues` missing values.

### replace missing values

```{r}
findmissingvalues <- which(is.na(activitydata$steps))

replace_data <- rep.int(mean(activitydata$steps, na.rm = TRUE),
                        times = length(findmissingvalues))
```

### create a new dataset where missing values filled in

```{r}
activitydata[findmissingvalues, "steps"] <- replace_data
```

### histogram
```{r}
totalsteps <- aggregate(activitydata$steps,
                        by = list(activitydata$date),
                        FUN = sum 
                        )

names(totalsteps) <- c("date","total")

hist(totalsteps$total, 
     main = "Total number of steps taken each day; replaced missing value",
     xlab = "Number of steps")

mean(totalsteps$total)
median(totalsteps$total)
```

## Differences in activity patterns between weekdays and weekends

```{r}
library(lattice)
activitydata$date <- as.Date(activitydata$date)

activitydata <- data.frame(date = activitydata$date,
                           weekday = tolower(weekdays(activitydata$date)),
                           steps = activitydata$steps,
                           interval = activitydata$interval)


activitydata <- cbind(activitydata,
                      daytype = ifelse(activitydata$weekday == "星期六" |
                                        activitydata$weekday == "星期日", "weekend", "weekday"
                                      ))

activitydata <- data.frame(date = activitydata$date,
                           activitydata$weekday,
                           activitydata$daytype,
                           activitydata$steps,
                           activitydata$interval)

names(activitydata) <- c("date", "weekday", "daytype", "steps", "interval")


```

```{r}
mean_data <- aggregate(activitydata$steps,
                       by = list(activitydata$daytype, 
                                 activitydata$weekday,
                                 activitydata$interval), FUN = mean)
names(mean_data) <- c("daytype", "weekday", "interval", "mean")

```

```{r}
xyplot(mean ~ interval | daytype, mean_data,
       type = "l",
       xlab = "Interval",
       ylab = "Steps number",
       layout=c(1,2),
)
```
